---
title: "Juliano E. Palacios Abrantes, PhD."
author: "Email: j.palacios@oceans.ubc.ca | Web Page: www.julianopalacios.com"
date: "Last updated, `r format(Sys.time(), '%B, %Y')`"
output:
  pdf_document:
    extra_dependencies: xcolor
    number_sections: true
header-includes:
   - \usepackage{hyperref}
---


<!-- Academic CV examples  -->
<!-- Elsevier... https://www.elsevier.com/connect/writing-an-effective-academic-cv -->

<!-- # Cover Letter -->

<!-- # Abstract -->

<!-- Juliano Palacios Abrantes' work looks at how climate change is shifting the distribution of marine species generating uncertain feedbacks on marine ecosystems and dependent fishing communities. Specifically, he looks at how such shifts affect shared stocks (e.g., stocks that are shared between neighboring states) threatening the sustainability of marine resources and accentuating sources of conflict. His work spans from global to local studies highlighting the need for adaptive, collaborative, equitable and ecosystem- based management strategies. Born in Brazil and raised in Mexico, he has a special interest in supporting ocean governance in the Latin American region. Juliano holds a bachelor's degree in Biology from the Metropolitan Autonomous University of Mexico City and a masters in environmental science and management from the Bren School at the University of California, Santa Barbara. He recently completed his PhD. here at the Institute for the Oceans and Fisheries with Dr. William Cheung and then worked as a postdoctoral researcher at the Center for Limnology of the University of Wisconsin, Madison. Currently, he works as a postdoctoral researcher at the Institute for the Oceans and Fisheries of the University of British Columbia, Canada. -->
<!-- \clearpage -->

# Academic Qualifications


- **Doctor in Philosophy; Zoology** (2021)
The Institute for the Oceans and Fisheries, University of British Columbia, Canada; Advisor, Dr. William Cheung
    -	*Transboundary Fish Stocks and their Management Under Climate Change*
    - Semester abroad at the University of Vigo working with Dr. Elena Ojea (August - December, 2019)

- **Master of Environmental Science and Management** (2016)
  Bren School of Environmental Science and Management, University of California at Santa Barbara, USA; Advisor, Dr. John Melack
    -	*A Citizen Science Monitoring Protocol for the Rocky Intertidal Habitat*
    - Internship at Environmental Defense Fund, Mexico (2015)
- **Bachelor of Science in Biology** (2012)
  Universidad Autónoma Metropolitana campus Xochimilco, México City; Advisor, Dr. Virginia Melo
    -	*Sea Cucumber as a Source of Macronutrients for Low-Income Coastal Communities in Mexico.*
    - Year abroad at the University of São Paulo, Brazil

**Keywords:** *Climate change; Fisheries management; Shared fisheries; Marine conservation: Data science; Multidisciplinary; Social-ecological systems*


# Professional Experience

```{r professional_experience, child = 'pro_exp.Rmd', eval = T}
```


# Relevant Scientific Publications

```{r sci_publi, child = 'sci_pub.Rmd', eval = T}
```

# Teaching Experience and Mentoring

```{r teaching, child = 'teaching.Rmd', eval = T}
```

# Invited Seminars

```{r seminar, child = 'seminar.Rmd', eval = T}
```

# Participation in Conferences and Workshops

```{r conference, child = 'conference.Rmd', eval = T}
```

# Funding acquisition
```{r funding, child = 'funding.Rmd', eval = T}
```

# Community Service
```{r community_service, child = 'community_service.Rmd', eval = T}
```

# Knowledge Mobilization

```{r knowledge_mob, child = 'knowledge_mob.Rmd', eval = T}
```

# Referees


\center

--- 

# Annex

\flushleft

\setcounter{section}{0}


# Professional Experience {#an_pro_exp}

```{r an_prof_exp, child = 'an_pro_exp.Rmd', eval = T}
```

# Scientific Publications {#an_sci_pub}

```{r an_sci_pub, child = 'an_sci_pub.Rmd', eval = T}
```

# Teaching Experience and Mentoring {#an_teaching}

```{r an_teaching, child = 'an_teaching.Rmd', eval = T}
```

# Invited Seminars {#an_seminar}

```{r an_seminars, child = 'an_seminar.Rmd', eval = T}
```

# Conferences and Workshops {#an_conference}

```{r an_conference, child = 'an_conference.Rmd', eval = T}

```

# Funding Acquisition {#an_funding}

```{r an_funding, child = 'an_funding.Rmd', eval = T}

```

# Community Service {#an_cmmunity_service}

```{r an_cmmunity_service, child = 'an_community_service.Rmd', eval = T}

```

# Knowledge Mobilization {#an_knowledge_mob}
```{r an_knowledge_mob, child = 'an_knowledge_mob.Rmd', eval = T}

```

# Other Experience {#an_other}

```{r an_other, child = 'an_other.Rmd', eval = T}

```