---
title: "Untitled"
output: pdf_document
---


```{r setup, eval = T}

MyFunctions::my_lib(c("bib2df","tidyverse","janitor"))


```

# Load bib file

```{r load_data, eval = T, echo = T}


df <- bib2df("/Users/jepa/gitHub/jpalacios/Data/export.bib",
             separate_names = TRUE) %>% 
  clean_names() %>% 
  select(-address,-annote,-note)
  
  

head(df)

```
# Journal analysis

## General trends

### Publications per year

This bar-graph shows the number of publications per year 

```{r}

df %>% 
  group_by(year) %>% 
  tally() %>% 
  ggplot() +
  geom_bar(
    aes(
      x = year,
      y = n
    ),
    stat = "identity"
  ) 

```

### Aggregated publications per year

This line-graph shows the aggregated number of publications per year 

```{r}

years <- df %>% 
  arrange(year) %>% 
  pull(year) %>% 
  unique()
  

df %>% 
  group_by(year) %>% 
  tally() %>% 
  group_by() %>% 
  summarise(n_agg = cumsum(n)) %>% 
  mutate(year = years) %>% 
  ggplot() +
  geom_area(
    aes(
      x = year,
      y = n_agg
    )
  ) 

```

## Specific trends

### Publications per journal

This graph shows the number of publications per year for each journal

```{r journal, eval = T}

df %>% 
  group_by(journal, year) %>% 
  tally() %>% 
  filter(!is.na(journal)) %>% 
  ggplot() +
  geom_point(
    aes(
      x = year,
      y = n
    )
  ) +
  facet_wrap(~journal)

```

## First Author General trends

```{r}

df_fa <- df %>% 
  unnest() %>% 
  group_by(bibtexkey) %>% 
  slice(1) %>% 
  # View()
  filter(str_detect(last_name, "Palacios"))
```


### Publications per year

This bar-graph shows the number of publications per year as a first author

```{r}

df_fa %>% 
  group_by(year) %>% 
  tally() %>% 
  ggplot() +
  geom_bar(
    aes(
      x = year,
      y = n
    ),
    stat = "identity"
  ) 


```

### Aggregated publications per year

This line-graph shows the aggregated number of publications per year 

```{r}

years <- df_fa %>% 
  arrange(year) %>% 
  pull(year) %>% 
  unique()
  

df_fa %>% 
  group_by(year) %>% 
  tally() %>% 
  group_by() %>% 
  summarise(n_agg = cumsum(n)) %>% 
  mutate(year = years) %>% 
  ggplot() +
  geom_area(
    aes(
      x = year,
      y = n_agg
    )
  ) 

```

# Specific trends

## Publications per journal

This graph shows the number of publications per year for each journal

```{r journal, eval = T}

df_fa %>% 
  group_by(journal, year) %>% 
  tally() %>% 
  filter(!is.na(journal)) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = year,
      y = n
    ),
    stat = "identity"
  ) +
  facet_wrap(~journal)

```

# Co-aturhos analysis

In this part I analyze the number of different collaborators I have had over time. Below shows the number of different collaborators from all my papers and from all the papers as first author

```{r}

data.frame(
"all_papers" = df %>% 
  unnest(author) %>% 
  filter(last_name != "Palacios-Abrantes") %>% 
  group_by() %>% 
  summarise(n = length(unique(last_name))) %>% 
  pull(),

"first_author" = df %>% 
  filter(bibtexkey %in% df_fa$bibtexkey) %>% 
  unnest(author) %>% 
  filter(last_name != "Palacios-Abrantes") %>% 
  group_by() %>% 
  summarise(n = length(unique(last_name))) %>% 
  pull()
)
```

This bar-graph shows the number of publications per year and author over 1

```{r}

df %>% 
  unnest() %>% 
  group_by(year,last_name) %>% 
  tally() %>% 
  filter(last_name != "Palacios-Abrantes",
        n > 1) %>% 
  arrange(n) %>% 
  ggplot() +
  geom_bar(
    aes(
      y = reorder(last_name,n),
      x = n
    ),
    stat = "identity"
  )
  

```

This bar-graph shows the number of different authors per year

```{r}

df %>% 
  unnest() %>% 
  filter(last_name != "Palacios-Abrantes") %>% 
  group_by(year) %>% 
  summarise(n = length(unique(last_name))) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = year,
      y = n
    ),
    stat = "identity"
  )
  
```
